The World Wide Web is accessible to anyone with an internet connection. But analyzing this vast amount of data to extract meaningful information is rather difficult because of its sheer volume. There have been a lot of research focusing on extracting content from the web to build large knowledge bases. For instance, extracting events and the associated entities from biomedical and molecular biology text has drawn a lot of attention, especially because of the introduction of BIONLP tasks targeting fine-grained information extraction.  The knowledge bases built by information extraction systems can find application in a variety of fields, for example, to supplement the structured information available to build quiesting answering systems.

In this paper, we focus on the task of event and entity extraction, with semantic role labeling. Most of the prior work either focuses on subsets of these tasks or look at very specific types of events or entities that are to be extracted. For instance, Toutanova et. al. focuses on entity extraction and semantic role labeing assuming that the event triggeres are known, while McClosky focuses on event and argument extraction for only binding, regulation and phosphorylation event types. These works show that the task of extracting information from text is possible with reasonable accuracy level.  But, the performance of the state-of-the-art systems is still quite distant to that of a ’perfect’ extraction system. This is mostly because interpreting meaning from complex structures of natural language is a hard task. In this work, we combine the representations, feature extraction methods and models adopted in the previous work.