\subsection{Argument prediction for triggers}
An entity is represented as a node in the parse tree spanning over the full text of the entity along the leaves of the tree. The fact that there is more than one event in almost all sentences makes our task of event-entity association harder. This is because, instead of just predicting a node in the parse tree as an entity, we have to predict if a node is associated with a specific trigger from task 1. To overcome this, we assign a probability for each node in the parse tree to be an entity associated with each event. Since this model was developed in parallel to the one in task 1, we are currently using the gold standard trigger words to denote events. Once we attain reasonable performance levels, we will use the predictions from step 1 to replace the gold standard. In addition, currently the model only tags if a node in the parse tree is associated with a specific event trigger or not. Since we are using a MaxEnt model, extending this to predict semantic role labeling would make it from a 2 class classification (Argument and None) to a multi-class classification (where the classes are the semantic roles like Agent, Theme, Destination, Origin, Result etc. and None).

As a first step, we built a baseline model that predicts a node in the parse tree as an argument to an event trigger, if it is of part-of-speech tag 'NP' and if the head word of the node in the parse tree is a child of the event trigger in the dependency tree of the sentence. We used Collins head finder algorithm to identify the headword of a parse tree node. We then implemented a MaxEnt based model using more features between the event triggers and the candidate nodes. The features we use include POS tag of node + POS tag of event trigger, headword of node + POS tag of event trigger, path from the node to the event trigger and an indicator feature denoting whether the headword of the node is a child of the trigger in the dependency tree. The model assigns a probability value for each node in the parse tree to be an argument to a specific event trigger.

{\bf Dynamic Program for non-overlapping constraint.} Since we predict a node in the parse tree as an argument to an event trigger or not, there are instances when predicted entities overlap. For instance, a sub-tree of a tree node already marked as an entity may also be tagged as an entity. To avoid this, we devised a bottom-up dynamic program that tags a node as entity or not, looking at the probability of the node and its immediate children being entities. We compute the scores for the following two scenarios:

\begin{enumerate} 
\item Tag the node as an entity: In this case, none of its children can be entities. The score in this case is the sum of the log probabilities of the node being an entity
\item Do not tag the node as an entity. In this case, the children can retain their class (Entity or None).The score is computed as the sum of the log probabilities of the node to be of class NONE and those of the child nodes to retain their class.
\end{enumerate}

Depending which of the scores computed above is higher, we assign the node to that class. Another addition we did to the dynamic program was that an entity node cannot subsume a node in the parse tree that is an event trigger. 