\subsection{Semantic Role Labeling}
For argument identification, we had used a binary classifier based on MaxEnt model that predicts a probabilty value it to be an argument. For semantic role labeling, we extended this model to a multi-class classifier to generate probability values for a parse-tree node to belong to the different semantic roles. We also modified the dynamic program for non-overlapping constraint used in argument prediction to a re-ranking model that jointly assigns semantic role to all nodes in a sub-tree. Let $L$ be labeling of semantic roles to the parse tree nodes, including $NONE$ if it is not an entity. Our goal is maximize the probability of the labeling we generate.\\

TODO - have a equation if possible.\\

We use a bottom up re-ranking approach by keeping the top-k joint assignment of semantic roles to all nodes in a sub-tree. This algorithm is similar to the dynamic programming for non-overlapping constraints. At the pre-terminal nodes, we keep just the semantic roles of the word subsumsed by the node in descending order of probability. At nodes above the pre-terminal nodes, there are two scenarios:

\begin{enumerate}
\item The node is an argument to the trigger: In this case, the node has a non-NONE semantic role and none of the children nodes can be entities and hence all children would have semantic role $NONE$. For each non-NONE semantic role of the node, we compute the probability value of the joint labeling of the sub-tree.
\item The node is not an argument to the trigger: In this case, the node has a semantic role of $NONE$. Since at each of the child nodes we have top-k possible assignements, we take all combinations of assignments of children nodes and compute the probability for each of these possible joint labelings.
\end{enumerate}

The next step is to re-rank all the possible joint assignments possible at the node and then retain only the top-k at the node. This algorithm proceeds until we reach the root and the joint labeling that has the highest probability will be the semantic roles predicted by the model.
