%
% File acl2013.tex
%
% Contact  navigli@di.uniroma1.it
%%
%% Based on the style files for ACL-2012, which were, in turn,
%% based on the style files for ACL-2011, which were, in turn, 
%% based on the style files for ACL-2010, which were, in turn, 
%% based on the style files for ACL-IJCNLP-2009, which were, in turn,
%% based on the style files for EACL-2009 and IJCNLP-2008...

%% Based on the style files for EACL 2006 by 
%%e.agirre@ehu.es or Sergi.Balari@uab.es
%% and that of ACL 08 by Joakim Nivre and Noah Smith

\documentclass[11pt]{article}
\usepackage{acl2013}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
%\setlength\titlebox{6.5cm}    % You can expand the title box if you
% really have to

\title{Event extraction using iterative optimization}

\author{
   Aju Thalappillil Scaria \\
  {\tt ajuts@stanford.edu} \\\And
  Rishita Anubhai \\
  {\tt rishita@stanford.edu} \\\And
  Rose Marie Philip \\
  {\tt rosep@stanford.edu} 
\\}

\date{}

\begin{document}
\maketitle
\begin{abstract}
\input{000abstract}
\end{abstract}

\section{Introduction}
\label{sec:introduction}
\input{010introduction}

\section{Previous Work}
\label{sec:previousapproaches}
\input{020previousapproaches}

\section{Data}
\label{sec:data}
\input{030data}

\section{Model}
\label{sec:model}
\input{040model_overview}
\label{sec:model}
\input{040model_trigger}
\label{sec:model}
\input{040model_argument}
\label{sec:model}
\input{040model_io}
\label{sec:model}
\input{040model_srl}

\section{Results}
\label{sec:results}
\input{050results}

\section{Analysis}
\label{sec:analysis}
\input{060analysis}

\section{Conclusion}
\label{sec:conclusion}
\input{070conclusion}

\section*{Acknowledgments}

Do not number the acknowledgment section. Do not include this section when submitting your paper for review.

%\bibliographystyle{acl}
%\bibliography{bibliography}
\begin{thebibliography}{}

\bibitem[\protect\citename{Chambers and Jurafsky} 2008]{chju2008}
Nathanael Chambers and Dan Jurafsky.
\newblock 2008.
\newblock Unsupervised learning of narrative event chains.
\newblock In {\em Proceedings of ACL-08}.

\bibitem[\protect\citename{Chambers and Jurafsky} 2009]{chju2009}
Nathanael Chambers and Dan Jurafsky.
\newblock 2009.
\newblock Unsupervised Learning of Narrative Schemas and their Participants
\newblock In {\em Proceedings of ACL-09}.

\bibitem[\protect\citename{Chambers and Jurafsky} 2011]{chju2011}
Nathanael Chambers and Dan Jurafsky
\newblock 2011.
\newblock Template-Based Information Extraction without the Templates
\newblock In {\em Proceedings of ACL-11}.

\bibitem[\protect\citename{Bjorne \bgroup et al.\egroup} 2009]{bjorne}
Jari Bjorne, Juho Heimonen, Filip Ginter, Antti Airola, Tapio Pahikkala, Tapio Salakoski
\newblock 2009.
\newblock Extracting Complex Biological Events with Rich Graph-Based Feature Sets.
\newblock In {\em Proceedings of the Workshop on BioNLP: Shared Task,}.

\bibitem[\protect\citename{Toutanova \bgroup et al.\egroup} 2005]{toutanova}
Kristina Toutanova, Aria Haghighi, Christopher D. Manning
\newblock 2005.
\newblock Joint Learning Improves Semantic Role Labeling.
\newblock In {\em Proceedings of ACL 2005}.

\bibitem[\protect\citename{Riedel and McCallum} 2008]{riedelmc}
Sebastian Riedel Andrew McCallum
\newblock 2008.
\newblock Fast and Robust Joint Models for Biomedical Event Extraction.
\newblock In {\em Proceedings of the 2011 Conference on Empirical Methods in Natural Language Processing}.

\bibitem[\protect\citename{Miwa \bgroup et al.\egroup} 2010]{miwa2010c}
Makoto Miwa, Rune Saetre, Jin-Dong D. Kim, and Jun’ichi Tsujii
\newblock 2010c.
\newblock Event extraction with complex event classification using rich features
\newblock In {\em Journal of bioinformatics and computational biology}.

\bibitem[\protect\citename{McCloskly \bgroup et al.\egroup} 2011]{mcclosky}
David McClosky, Mihai Surdeanu, and Christopher D. Manning
\newblock 2011.
\newblock Event Extraction as Dependency Parsing
\newblock In {\em Proceedings of ACL-11}.

\bibitem[\protect\citename{Chambers and Jurafsky}{2008-temporal ordering}]{temporalordering}
Nathanael Chambers and Dan Jurafsky
\newblock 2008.
\newblock Jointly Combining Implicit Constraints Improves Temporal Ordering
\newblock In {\em EMNLP-08}.

\bibitem[\protect\citename{McCloskly \bgroup et al.\egroup} 2012]{quang}
Quang Xuan Do, Wei Lu, Dan Roth
\newblock 2012.
\newblock Joint Inference for Event Timeline Construction
\newblock In {\em EMNLP-12}.

\end{thebibliography}
\end{document}
